% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Gambling Night on S/V Gina},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\title{Gambling Night on S/V Gina}
\author{}
\date{}

\begin{document}
\maketitle

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Party Info

  \begin{enumerate}
  \def\labelenumii{\alph{enumii}.}
  \item    Location: 2000 Glen Cove Marina Drive, Pier 7, slip 173.
  \item Capacity Limit: 4 guests plus Joey as host, 5 persons overall.
  \item Food and Drink: Not BYOB but sharing is caring. If you're going to
    drink, consider bringing a bottle of cheap wine or a six pack, or a
    snack or something.
  \item Playing Money: Bring \$10 cash to buy chips. Denominations are: red
    33c, white \$1, green \$3, black \$9.

    \begin{enumerate}
    \def\labelenumiii{\roman{enumiii}.}
    \item
      Note, I don't have coins. If your balance at the end is \$8.33,
      I'll give you eight ones and you'll have donated 33 cents to
      keeping the lights on.
    \end{enumerate}
  \item
    Bathroom: there is a head on the boat, but I recommend using the one
    in the bathhouse in the parking lot on the way in. Codes: Men's 1245
    Women's 1235
  \end{enumerate}
\item
  The rules of the game

  \begin{enumerate}
  \def\labelenumii{\alph{enumii}.}
  \item
    After the players have bought chips, assign one person to be the
    dealer. Probably me.
  \item
    Dealer shuffles and cuts a standard 52 card deck.
  \item
    The person to dealer's left sets the ante, usually one red chip.
    They must do this blindly, and dealer's left must play. Clockwise,
    players ante in, matching the initial ante set by the blind, if they
    wish to receive cards. A player may choose not to ante, and they
    will get no cards. Maximum ante 1 white chip.
  \item
    The dealer deals, face down, 3 cards to each player who antes in,
    plus a hand of three to ``the ghost''. After all players and the
    ghost have three cards in their hands, the dealer places one card
    face up on top of the deck to indicate the trump suit.
  \item
    Everyone can pick up their cards. Starting on the dealer's left and
    going clockwise, each player decides if they want to play. The
    possible actions are fold, call, or ghost.

    \begin{enumerate}
    \def\labelenumiii{\roman{enumiii}.}
    \item
      If a player folds, they place their hand, faces down, on the
      table, and say they fold. They do not recoup their ante, they do
      not play in the next phase of the game, they are safe from being
      looed.
    \item
      If a player thinks they have good cards, they may call or raise.
      To call, place 1x ante into the pot. A player may also raise up to
      3x ante when it's their turn to do so. Any subsequent player
      wishing to remain in must call or raise.

      \begin{enumerate}
      \def\labelenumiv{\arabic{enumiv}.}
      \item
        Example, Dan is Dealer. Alice sets ante at 33 cents and everyone
        antes in. Dan Deals. Alice calls, throwing in 33 cents. Bob
        raises by one dollar (3x ante) and puts in 1.33. Charlie Raises
        66 cents 2x ante) and puts in two dollars. Dan folds, Alice
        wants to stay in and puts in 1.66 for a total of two dollars,
        Bob wants to stay in and puts in 66 cents for a total of two
        dollars. Pot is 7.33.
      \end{enumerate}
    \item
      A player may take the ghost's hand. They lose the right to fold or
      raise, only to call. They call (deposit 1x ante into pot) and swap
      their cards with the ghost's cards. If the ghost has 3 twos, you
      cannot chicken out, you must stay in, and must match any raises.

      \begin{enumerate}
      \def\labelenumiv{\arabic{enumiv}.}
      \item
        As a house rule multiple people can swap. If Max throws away her
        cards to take the ghost hand, I can still think that my cards
        are so bad that I would rather have what she threw away.
      \end{enumerate}
    \end{enumerate}
  \item
    When the betting phase is done, the trick taking portion begins.

    \begin{enumerate}
    \def\labelenumiii{\roman{enumiii}.}
    \item
      If only one person calls, they take the pot by default.
    \end{enumerate}
  \item
    The last person to call is the first to throw in a card, face up, to
    the center of the table. This card sets the suit. This card cannot
    be the jack of clubs on the first round.
  \item
    Going clockwise, each player puts down one card. The player with the
    highest card wins the trick, and keeps the cards played in a pile
    near their money for scoring.

    \begin{enumerate}
    \def\labelenumiii{\roman{enumiii}.}
    \item
      Card Ranks, from highest to lowest: Jack of Clubs; Trump suit,
      AKQJ 10 9 8 \ldots{} 2, initial suit AKJQ10 9 8 \ldots{} 2, any
      other suit loses.
    \end{enumerate}
  \item
    Scoring and Distribution. If you win a trick you win one third of
    the pot.

    \begin{enumerate}
    \def\labelenumiii{\roman{enumiii}.}
    \item
      House rule, In the event that one player wins 2/3rds and another
      wins 1/3rd, and the pot is not a threeven number, the player that
      wins less keeps the change, i.e. 10 split 6 and 4 not 8 and 2
    \end{enumerate}
  \item
    Any player who takes zero tricks must match the entire pot.

    \begin{enumerate}
    \def\labelenumiii{\roman{enumiii}.}
    \item
      Using the example from Above, where Alice, Bob, and Charlie are
      in, but Dan folded, and the pot was 7.33 to start: Alice won two
      tricks, Bob won one, Charlie won none (Charlie got looed). Charlie
      adds 7.33 to the pot for the next game, Bob wins 2.66, Alice wins
      4.66. For the next round, when Alice is the dealer and Bob is the
      blind, the pot is 7.33+antes+calls and raises. If 4 people are
      playing, and all 4 call every time, the pot can get pretty big
      even if each time everyone but the 4\textsuperscript{th} person
      takes one trick. Knowing when to fold is important.

      \begin{enumerate}
      \def\labelenumiv{\arabic{enumiv}.}
      \item
        House Rule, you can never go negative. If Charlie only had \$5
        in reserve in the scenario above, Charlie puts in all 5 dollars
        and is out. If Charlie buys more chips, they do not have to put
        2.33 into the pot. They can re-enter play on the following game.
      \end{enumerate}
    \end{enumerate}
  \item
    Lastly, don't let it get too scary or too real. We're a low limit
    table for a reason, and it's not just because we can't afford eggs.
    All of us are friends, we mustn't get into a fight.
  \end{enumerate}
\end{enumerate}

\end{document}
