\documentclass[12pt,letterpaper,draft]{memoir}
\usepackage{memhfixc}
\usepackage[hidelinks]{hyperref}
\usepackage[margin=1in]{geometry}
\author{cocainagrif}
\date{}
\title{Feyd-Rautha Accepts His Punishment (Dune, casual snuff, reluctant killer, slavery, semi-cons, decap, asphyx)}
\begin{document}
\maketitle
Slowly, Feyd-Rautha wet his lips with his tongue. Could it be true what the old fool was saying? There was more here than there seemed to be.\\
“And what has Hawat to do with this?” Feyd-Rautha asked.\\
“He thinks he uses us to wreak his revenge upon the Emperor.”\\
“And when that’s accomplished?”\\
“He does not think beyond his revenge. Hawat’s a man who must serve others, and doesn’t even know this about himself.”\\
“I’ve learned much from Hawat,” Feyd-Rautha agreed, and felt the truth of the words as he spoke them. “But the more I learn, the more I feel we should dispose of him\ldots and  soon.”\\
“You don’t like the idea of his watching you?”\\
“Hawat watches everybody.”\\
“And he may put you on a throne. Hawat is subtle. He is dangerous 
devious. But I’ll not yet withhold the antidote from him. A sword is dangerous, too, Feyd. We have the scabbard for this one, though. The poison’s in him. When we withdraw the antidote, death will sheathe him.”\\
“In a way, it’s like the arena,” Feyd-Rautha said. “Feints within feints within feints. You watch to see which way the gladiator leans, which way he looks, how he holds his knife.”\\
He nodded to himself, seeing that these words pleased his uncle, but thinking: \textit{Yes! Like the arena! And the cutting edge is the mind!}\\
“Now you see how you need me,” the Baron said. “I’m yet of use, Feyd.”\\
\textit{A sword to be wielded until he’s too blunt for use}, Feyd-Rautha thought.\\
“Yes, Uncle,” he said.\\
“And now,” the Baron said, “we will go down to the slave quarters, we two. And I will watch while you, with your own hands, kill all the women in the pleasure wing.”\\
“Uncle!”\\
“There will be other women, Feyd. But I have said that you do not make a mistake casually with me.”\\
Feyd-Rautha’s face darkened. “Uncle, you—”\\
“You will accept your punishment and learn something from it,” the Baron said.\\
Feyd-Rautha met the gloating stare in his uncle’s eyes. \textit{And I must remember this night, he thought. And remembering it, I must remember other nights.}\\
“You will not refuse,” the Baron said.\\
\textit{What could you do if I refused, old man?} Feyd-Rautha asked himself. But he knew there might be some other punishment, perhaps a more subtle one, a more brutal lever to bend him.\\
“I know you, Feyd,” the Baron said. “You will not refuse.”\\
\textit{All right}, Feyd-Rautha thought. \textit{I need you now. I see that. The bargain’s made. But I’ll not always need you. And\ldots someday \ldots} 
\end{document}
