\documentclass{article}[letterpaper,12pt]
\usepackage{inputenc}[utf8]
\usepackage{csquotes,xpatch}
\usepackage[backend=biber, style=apa]{biblatex}
\addbibresource{leadership.bib}
\usepackage{hyperref}
\usepackage[shortlabels]{enumitem}
\usepackage[margin=1in]{geometry}
\usepackage{pdfpages}
\author{Joey Simone}
\title{Lifelong Learning \& Leadership Assignment}
\date{Monday, April 22}
\begin{document}
\maketitle
\begin{verbatim*}
	ResultID:7f6d1c04-a57e-4ec6-a0a6-c4451e654d78
\end{verbatim*}
\begin{enumerate}
	\item My Top Core Values according to the website are\parencite{noauthor_your_nodate}: 
		\begin{enumerate}[i.]
			\item Accountability
			\item Financial Stability
			\item Challenge
			\item Control
			\item Competence
		\end{enumerate}
	\item I'm most surprised about what values aren't in the top 5. I'm a boy scout, I'm supposed to be Trustworthy, Loyal, Helpful, Friendly, Courteous, Kind, Obedient, Cheerful, Thrifty, Brave, Clean, and Reverent. I know I saw those in the overall list of values (except maybe "clean"), but the only one I actually got on the board was Thrifty, vis-a-vis ``Financial Stability''. Accountability is a no-brainer for me, nobody keeps a stricter accounting of my worth and contribution than myself. Financial Stability and Control, I think, have entered my values because I have spent the last 3 or so years desperately lacking both, constantly being run ragged by those who have control over me, and being desperately broke at the end of every month. Challenge and Competence have been big drivers of motivation for me at this school and out of it to become the best person I've ever been. My overwhelming competence has preserved me from being spoken negatively of at this school. I'm a member of like 3 minorities, and my friends who are members of those same minorities tell me about the issues they face, but I am so good at celestial navigation that I have a get-out-of-transphobia free card.
	\item Achieving Financial Stability will come almost immediately after graduating. My spending amount won't go up as fast as my income goes up. I just have to pay off my debts and put the rest into a mutual fund. I always see getting new tasks at work as a challenge, and I constantly keep up my competence. I think that in accountability I need to give myself more credit.
	\item Being a junior officer may present a challenge to control. I have to have some control, but not as much as the Chief Mate or the Captain, and it may not be acceptable to give a command to the Boatswain. It may be difficult to achieve financial stability if my addictive personality gives me some expensive habits. 
	\item I don't really have a 5 year plan beyond "work for MSC, get union time, get sea time, get paid, payoff all my debt, invest my money, spend my ashore time singing, become second mate, maybe take the Chief Mate's exam." I don't know if this existing plan conforms to all of the values that bubbled to the top of this list, but I can tell that Financial Stability, Competence, and Challenge are satisfied. Maybe the lack of detail in the 5 year plan shows a lack of control? I'm happy to let the wind (my orders) take me to far flung environs for who knows how long. I won't be able to accomplish that plan without accountability. Maybe this plan does satisfy all the values. I didn't mention love or family or the other things I suspect people do because I don't really expect to have them.
	\item My five strongest leadership qualities, to me, are:
		\begin{enumerate}[i.]
			\item "4. Always Teaches:"\parencite{peitzman_20_2022} This quality is so strong in me and important to me that it is already my on campus job, and it was my first full time job. I'm a tutor, I taught sailing and merit badges and I was a lifeguard instructor. I have helped so many people academically as a tutor, and I intend to help everyone on my ships be the best mariners they can be. Teaching and helping is how I show I care, and I will never stop doing it.
			\item "8. Focus." \parencite{wike_20_2023} I have been promoting ``SMART Goals'' in the groups that I've led since the boy scouts. I also have focus in the other sense, that my dedication to completing a task will mean that I have to finish it even if it destroys my body.
			\item "10. Eager to learn"\parencite{wike_20_2023} You definitely know this to be true about me. I need to learn more all the time, it's an itch that never goes away.
			\item "18. Self-awareness"\parencite{wike_20_2023} Nobody is more aware of my limitations than me. I know all of my weaknesses.
			\item "14. Acknowledges effort and results:"\parencite{peitzman_20_2022} Tutoring sessions and ship ops are awful for both me and the other person when I fail to recognize their effort, growth, and results.
		\end{enumerate}
	\item I think that my strength in leadership has always been making other people better. I am best as a second in command or an adviser, and I always did terribly as the top dog. I am an enabler of greatness. My gift to those under me and over me is that I make their work easier, I never need help doing my work, and I can help them be the best at their jobs.
	\item I wish I was better at compassion and empathy. It is \emph{so} easy to harbor or even voice negative opinions of others at a time that they are low, and it takes actual effort to not do this because deep down inside I'm a bad person. Empathy is about feeling what someone else is feeling and I've never been able to. I do the right thing, I help them, I pretend to feel, but I never feel it. I also wish I could avoid distractions. My ADHD gets the best of me at the worst moments and takes me off a train of thought in a terrible way. My active listening skills are also in a bad way. I am so good at talking over women it's staggering, like I have a 6th sense for when a woman is about to start talking. It's a bad thing and I need to stop. Like literally count in my head for 4 seconds before I say anything in class and group environments. 
\end{enumerate}
\printbibliography
%\includepdf[pages=-]{Lifelong Learning Assignment - Tagged.pdf}
\end{document}
